Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-30 doc/om-paper/paper.tex
added table for extensions.

\subsection{Modular Verification}\label{sec:modular}
To demonstrate the modularity of the model and verification approach, in this section, we explore variants to the model and discover the effort required to implement the modifications and repair the proofs.

%% \begin{figure}
%%   \centering
%%   \begin{tabular}{r|l|l|l|}
%%                    & Modules modified    & Lemmas modified & Lemma classes modified\\
%%   \hline \hline
%%   Faults           & 
%%   \hline
%%   Time-triggered   &
%%   \hline
%%   \end{tabular}
%%   \caption{Refactoring effort for protocol modifications.}
%%   \label{fig:effort}
%% \end{figure}

\paragraph{Modified fault model.}

>>>>

\subsection{Modular Verification}\label{sec:modular}

\begin{figure}
  \centering
  \begin{tabular}{p{3cm}|p{3cm}|l|l|}
                                  & Modules modified    & Lemmas modified & Lemma classes modified\\
  \hline \hline
  Byzantine-only fault model      & 0                   & 0               & 0 \\
  \hline
  Time-triggered message-passing  & \texttt{clock}, \texttt{relay}
                                  , \texttt{receiver}   & 0               & 0 \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications.}
  \label{fig:effort}
\end{figure}
To demonstrate the modularity of the model and verification approach, in this section, we explore variants to the model and discover the effort required to implement the modifications and repair the proofs. The results are summarized in Figure~\ref{sec:effort} and sketched below.

\paragraph{Fault model.}
Modifying the fault model is easy. In involves modifying the definition of a single function, \texttt{mfa}, that takes as an argument the static assignment of node identifiers to faults. Moreover
